\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

% SUBSUBSECTION FORMATTING
\titlespacing*{\subsubsection}{0em}{0em}{0em}
\titleformat{\subsubsection}{\itshape}{}{0em}{}[]

%====================

\subsection{ColorTokens Inc. - Xcloud \& Xshield NextGen teams (Cyber Security)\hfill Bengaluru, India}
\subtext{{Member of Technical Staff - III (DevOps \& Backend) \hfill July 2022 --- Current}}
\begin{zitemize}
\item Developed Zero-Trust security analysis workflow on kubernetes clusters for CSPM on AKS, EKS, GKE platforms.
\item Developed DHCP relay server to perform network micro-segmentation.
\item Converting monolith services running on AWS EC2 and AWS Lambda into kubernetes microservices.
\item Building hardened docker images (approved by IronBank) for enhanced security.
\item Deploying and managing on-premise, air-gapped kubernetes clusters on Vsphere and AWS for various clients.
\item Integrating secrets management with key-rotation support using Hashicorp vault on kubernetes.
\item Configuring inter-service communication using kong and istio.
\item Setting up modular terraform for multi-region cluster and microservices deployment in on Azure, AWS.
\item Setting up CI/CD pipelines on Jenkins \& Azure DevOps.
\item Experience using multiple AWS/Azure cloud services like Codebuild, EKS, S3, VPC, EC2, ELB, IAM, SES, CloudWatch etc.
\end{zitemize}

%====================

\subsection{Auquan Ltd. (Finance Sector) \hfill Bengaluru, India (Part-time)}
\subtext{{Sr. Full-Stack Engineer\hfill May 2021 --- July 2021}}
\begin{zitemize}
\item Building data pipelines for financial news collection from several search engines
\item Redesigned interface for complex graph visualizations between entities
\item Maintaining and deploying data pipelines to AWS ECS 
\end{zitemize}

%====================

\subsection{Viper Development UG [now FounderBlocks] (Multiple sectors) \hfill Hamburg, Germany}
\subtext{{Sr. Full-Stack Engineer \hfill July 2018 --- June 2022}}

\vspace{1em}
\subsubsection*{Skynet MCANISM (Ad-tracking platform)}
\begin{zitemize}
\item Improved API response times by 20 times on report generation pipelines
\item Reduced database clutter with flat hypertables using time-partitioning on TimescaleDB
\item Designed a reusable filtering architecture in django for report generation
\item Managed container orchestration using kubernetes and deploying final applications on GCP
\item Actively participated in data recovery, production release monitoring, rollback and debugging k8s microservices on GCP
\item Worked on scripts for CI/CD pipelines, database snapshots, blob storage backups and access key rotation
\end{zitemize}

\subsubsection*{Pandas ZF (Human Machine Interfaces)}
\begin{zitemize}
\item Developed a real-time IOT focused web application to collect telematics information from automobile suspension kits
\item Extended the real-time data platform to provide historical ride quality information on selected roads
\end{zitemize}

\subsubsection*{myndpaar.de (Mental Health / Counselling)}
\begin{zitemize}
\item Wire-framing and building a cross platform mobile application for couples counseling in association with myndwerk GmbH
\item Engaging users to perform various activities using automated push notifications
\item Added in-app payments support for monthly subscriptions
\end{zitemize}

\newpage

%====================

\subsection{GitMate UG (Developer tools) \hfill Hamburg, Germany (Part-time)}
\subtext{{Full-Stack Engineer / Developer Tools \hfill Dec 2016 --- July 2018}}
\begin{zitemize}
\item Helped in building a multilingual code linter that supports multiple languages using a single config file
\item Built a linting and codesmell detection pipeline from scratch to manage continuous integration for several customers
\item Designed an open-source reusable plugin architecture to link the linting pipeline to several cloud based Git-hosting services
\item Worked on a duplicate issue detection plugin to identify closely matching issues on GitHub projects
\end{zitemize}

%====================

\subsection{Wipro Business Solutions (Internship) \hfill Bengaluru, India}
\subtext{{Software Engineering Intern \hfill May 2017 --- June 2017}}
\begin{zitemize}
\item Designed a native Android application to manage ONVIF compliant cameras
\item Added Android Auto support to connect with rear parking cameras in automobiles
\end{zitemize}

%====================

\end{document}
